\chapter{Acknowledgments}

It takes a village to raise a child, and apparently to raise a Ph.D. as well. My graduate career has been marked by uncountable people who have given me the energy, support, and confidence to keep going in the graduate program over the last five-and-a-half years. I hope they know who they are, and I will try to list as many as I can here.

First and foremost, I want to thank my advisors for taking me on as a student. To Jonathan Katz, who took me on with only limited experience in cryptography; and Giulio Malavolta, who agreed to co-advise me as a relative unknown. Even though I was constantly coming and going, Jon and Giulio always answered when I reached out with questions and supported me in applying to internships, traveling to conferences, etc. Thanks also to Gilles Barthe, my first advisor at MPI-SP, who was patient with me when I was still trying to figure out what sort of security and privacy research I was interested in, helped put me in Giulio's hands, and continued to be willing to support me even when I was no longer his student. And thank you to Duncan Buell, who, back in 2015, convinced me to study math and computer science.

I am grateful to the National Science Foundation for the Graduate Research Fellowship which helped fund me during most of graduate school, and to the Maryland-Max Planck program for allowing me to travel widely, meet people from all over the world, and collaborate across many institutions. I am also indebted to NTT Research and a16z crypto for amazing internship experiences which had a great effect on shaping my research agenda and led to a large portion of the research in this dissertation.

The wider faculty at UMD, MPI-SWS, MPI-SP, and Bocconi University also left a mark as role models, lunch and coffee companions, and by dispensing occasional doses of wisdom and experience. The same goes for the researchers and visitors at NTT Research and a16z crypto who I had the privilege of coming into contact with during my summer internships. Thank you especially to all of my coauthors, each of whom taught me something new about how to do and present great research. Finally, I am grateful to the other students and young researchers I met at these institutions or through these internships, research visits, and conferences for creating a kind, fun, and supportive research community. In particular, I want to thank Erica Blum, Miranda Christ, Jason Fan, Phillip Gajland (and the rest of the kicker squad at MPI-SP), Doruk G\"ur, Lillian Huang, Hannah Keller, Hunter Kippen, Lisa Masserova, Vedant Nanda, Michael Rosenberg, Istv\'an Seres, Noel Warford, and the Bocconi Clowns (Damiano Abram, Pedro Branco, Ruta Jawale, Darya Kaviani, Tamer Mour, and Nikolaj Schwartzbach).

On the personal side, thank you to my family, especially my parents for being my biggest fans and always encouraging and supporting me in my endeavors, and my sister Tullia for her pragmatism and reminding me when things don't merit my constant worrying. Thanks also to my many flatmates over the last five and a half years who always made my various houses (some seven or eight of them) feel like homes; and especially Sarah, who reminds me to eat and sleep even when I feel very overwhelmed. Thank you to my friends (especially Joelle, Liz, and No\'emie; Marie and Marisa; Makana; and Spyral), who remind me I'm a whole person and not just a grad student. 

On a technical level, thank you to Alex Block and Doruk G\"ur for feedback on naysayer proofs for FRI (\Cref{sec:fri_naysayer}) and Dilithium (\Cref{sec:pqsig_naysayer}), respectively, and to Joe Bonneau, Jonathan Katz, Giulio Malavolta, and Istv\'an Seres for proofreading and comments on larger sections of this dissertation.