\section{The Cicada Framework}\label{sec:cicada_framework}

We present Cicada, our framework for non-interactive private auctions/elections, in \Cref{fig:cicada}. Cicada can be applied to voting and auction schemes where the scoring function $\Score = f \circ t$ has a linear tally function $t$. The framework uses a linear HTLP (\Cref{sec:tlp}), a vector packing scheme (\Cref{sec:packing}), and matching NIZKs (which we present in \Cref{sec:sigmas}) to ensure correctness of submissions by proving both the well-formedness of the puzzle and the solution's membership in $\X$.

\input{cicada/model}

Cicada implements a time-locked auction/voting scheme (\Cref{def:syntax}) as follows:
(0) System participants agree on a delay parameter $\timeT$ and packing parameter $\ell$. The latter introduces a crucial design choice, defining a storage-computation trade-off we detail in~\Cref{sec:cicada_eval}. The coordinator (or a set of trusted parties, depending on the HTLP construction used) runs the $\Setup$ algorithm to output HTLP public parameters $\pparam$ and initialize a (set of) aggregate HTLP(s) $\Z$ containing zeros. 
(1) A user $i$ runs the $\Seal$ algorithm to encode their submission (a bid or ballot) $\vec{v}_i$ into (a set of) HTLP(s) $\Z_i$. $\Seal$ also outputs a NIZK $\pi_i$ proving that $\Z_i$ is well-formed, i.e., its contents are in the domain $\X$ of the scoring function $\Score$. Users send their submissions and proofs to the on-chain coordinator. 
(2) Upon receiving a user submission $\Z_i, \pi_i$, the coordinator (Cicada smart contract) runs $\Aggr$ to verify $\pi_i$, and if it is valid, aggregates $\Z_i$ into the tally HTLPs $\Z$, resulting in updated tally $\Z'$. 
(3) After the voting/bidding period has ended, any party can open the tally HTLPs $\Z$ off-chain by running $\Open$, which outputs the opening(s) $\vec{s}$ of the tally HTLP(s) $\Z$ along with a proof of correct opening $\pi_{\textsf{open}}$ (using a proof of solution $\pos$, see \Cref{sec:sigmas}). The off-chain solver will send $\vec{s}, \pi_{\mathsf{open}}$ to the contract. 
(4) The on-chain contract runs $\Finalize$ to verify the correctness of $\vec{s}$ by checking $\pi_{\mathsf{open}}$. If the check passes, it computes the auction/election winner(s) as $y=f(\vec{s})$.

\input{cicada/protocols/cicada}

\paragraph{Additive voting}
Cicada captures ``additive'' voting schemes, meaning each ballot (a length-$m$ vector) is simply added to the tally, and a finalization function $f$ is applied to the tally after the voting phase has ended to determine the winner. 
This includes many popular voting schemes such as first-past-the-post (FPTP), approval, range, and cumulative voting. Simple ranked-choice voting schemes, e.g., Borda count~\cite{Emerson13}, are also additive, differing only in what qualifies as a ``proper'' ballot (restrictions on vector entries, norm, etc.; see \Cref{tab:voting_schemes}). 
Thus, Cicada can instantiate fair voting protocols for all these schemes.

\paragraph{Sealed-bid auctions}
The Cicada framework can also be used to implement a sealed-bid auction with a number of HTLPs which is independent of the number of participants $n$. 
Assuming bids are bounded by $M$, we use an HTLP with solution space $\X$ such that $\sizeof{\X} > M^n$.
Each user $i$ submits $Z_i \gets \htlp.{\sf Gen}({bid}_i)$ and $\pi_i$, where $\pi_i$ proves $0 \leq {bid}_i \leq M$. A packing of the bids is computed at aggregation time, with $\Aggr$ updating $Z$ to $Z \boxplus (M^{i-1} \cdot Z_i)$. After the bidding phase, the final ``tally'' is opened to $s^*$ and the bids are recovered as ${\sf Bids} := \{ s^* \mod{M^{i-1}} \}_{i \in [n]}$. Any payment and allocation function can now be computed over the bids; in the simplest case, the winner is $\argmax_i ({\sf Bids})$ and their payment is $\max_i ({\sf Bids})$. Here, the full set of bids is revealed after the auction concludes since $\max_i$ is a nonlinear function and cannot be computed homomorphically using linear HTLPs.

Locking up collateral is necessary for every (private) auction scheme. We treat the problem of collateral lock-up as an important but orthogonal problem and refer to~\cite{CCS:TAFWBM23} for an extensive discussion.

\subsection{Security Proof of Cicada}
Intuitively, submission privacy follows from the security of the HTLP (assuming the delay $\timeT$ is longer than the submission phase) and the zero-knowledge property of the NIZKs: the submission can't be opened before time $\timeT$ and none of the proofs leak any information about it. Non-malleability is enforced by requiring the NIZK to be a proof of knowledge and including the user's identity $i$ in the instance to prove, e.g., including it in the hash input of the Fiat-Shamir transform. This prevents a malicious actor from replaying a different user's ballot correctness proof.

\begin{theorem}\label{thm:cicada}
    Given a linear scoring function $\Sigma$, a secure NIZKPoK $\NIZK$ and proof of solution $\pos$, a secure $\htlp$, and a packing scheme $(\PSetup,\allowbreak \pack,\allowbreak \unpack)$, the Cicada protocol $\Pi_\Sigma$ (\Cref{fig:cicada}) is a secure time-locked voting/auction protocol. % i.e., it satisfies correctness, bid/ballot privacy, and non-malleability.
\end{theorem}

\begin{proof}
\def\Exp{\ensuremath{\mathsf{ExpSPriv}_{\Pi_\Sigma}^\adv(\secpar,\timeT,i)}}
    For simplicity, we give a proof for the simple case of $\X=[0,1]$, i.e., submissions consist of a single bit, but our argument generalizes to larger domains $\X$. Let $n \in \mathbb{N}$ be the number of users.

    The correctness of the Cicada framework (cf.~\Cref{def:correctness_cicada}) follows by construction and from the correctness of the underlying building blocks (i.e., soundness in the case of the proof systems).
    
    Next, we prove submission privacy.
    Let $\Exp$ be the original submission privacy game for the Cicada scheme $\Pi_\Sigma$ with $\timeT$-bounded adversary $\adv$, cf.~\Cref{def:submission_privacy}. We define a series of hybrids to show that 
    \[ 
        \Pr[\Exp = 1] \leq \negl 
    \]
    for all $\secpar,\timeT \in \mathbb{N}$ and $i\in[n]$.
    
    \underline{$\hybrid_0$:} This is the original game $\Exp$, where $Z_i \gets \htlp.{\sf Gen}(b)$ and $\pi_i \gets \NIZK.\prove(i, Z_i, b)$.
    
    \underline{$\hybrid_1$:} Replace $\pi$ with $\tilde{\pi} \gets {\sf NIZK}.\Sim(i, Z_i)$. $\hybrid_1$ is indistinguishable from $\hybrid_0$ by the zero-knowledge property of $\sf NIZK$.

    \underline{$\hybrid_2$:} Replace $Z_i$ with $Y_i \gets \htlp.{\sf Gen}(1-b)$ and $\tilde{\pi}$ with $\tilde{\sigma} \gets {\sf NIZK}.\Sim(i, Y_i)$. $\hybrid_1$ and $\hybrid_2$ are indistinguishable because the distributions $\{Z_i, \Sim(i, Z_i)\}$ and $\{Y_i, \Sim(i, Y_i)\}$ are indistinguishable since $\{Z_i\}, \{Y_i\}$ are indistinguishable by the security of $\htlp$.

    \underline{$\hybrid_3$:} Replace $\tilde{\sigma}$ with $\sigma \gets \NIZK.\prove(i, Y_i, 1-b)$. $\hybrid_3$ is indistinguishable from $\hybrid_2$ by the zero-knowledge property of $\sf NIZK$.

    This series of hybrids implies $\Pr[b'=b] \approx_\secpar \Pr[b'=1-b]$, where $b'$ is the output of $\adv$ in $\hybrid_0$ or $\hybrid_3$, respectively. Therefore $\Pr[\Exp = 1] \leq \frac{1}{2} + \negl[\secpar]$.
    
    Finally, we show that if $\NIZK$ is a PoK and $\htlp$ is secure, then Cicada is non-malleable (\Cref{def:non_malleability}). Suppose towards a contradiction that Cicada is malleable. We will use this and the fact that $\NIZK$ is a PoK to construct an adversary $\bdv$ which has non-negligible advantage in the $\htlp$ security game. Again, we work in the simple case $\X = [0,1]$, i.e., $m,\ell,w=1$, but the argument generalizes to other parameter settings.
    
    Since by our assumption Cicada is malleable, there exists $\adv$ which outputs $(i, \cdot, \Z_i, \pi_i) \notin \mathcal{Q}$ such that $\NIZK.\vrfy((i,\allowbreak \Z_i), \pi)=1$ with non-negligible probability. 
    % Also, $\sf NIZK$ is a PoK, so it has an efficient knowledge extractor $\Ext$. 
    Given a puzzle $Z_b$ containing some unknown bit $b$, $\bdv$ works as follows. First, it computes $(\pparam, Z) \sample \Setup(\secparam, \timeT, 1)$ and sends them to the non-malleability adversary $\adv$. $\bdv$ responds to $\adv$'s oracle queries $(j, b_j)$ with honestly computed $(Z_j, \pi_j)$, keeping track of queries and responses in the set $\mathcal{Q}$. When $\adv$ outputs $(i, Z_i, \pi_i)$, $\bdv$ looks for $(i, b_i, Z_i, \pi_i) \in \mathcal{Q}$ and outputs $b_i$. Since $\adv$ has non-negligible advantage, it follows that $\NIZK.\vrfy((i, Z_i), \pi_i) = 1$. This implies that either $\Pr[b_i=b] = \frac{1}{2} + \negl[\secpar]$ or $\NIZK$ is not knowledge sound. Both possibilities contradict our assumptions, namely that the $\htlp$ is secure and the $\NIZK$ is knowledge sound. Thus, Cicada must be non-malleable.
\end{proof}